---
title: "Workflow"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(bookdown)
library(rmarkdown)
```


This is a workflow to create the "reproduceability" we learned in the Summer School "Reproducable Research in Landscape Archaeology" by Ben Marwick et al. 17th-21st July 2017.


# Setup

Start Rstudio and start by creating your package:

```{r , eval=FALSE}
devtools::create("packagename") 
```
This creates also the description, namespace and manuals-folder (man).
Remember to edit the description. Especially the imports should be continously updated!

Levae the other two alone...

```{r, eval = FALSE}
devtools::use_mit_license()
```
This puts the MIT licence in the DESCRIPTION and creates the license-document, which you need to edit to give your name. Think about your decision, do you want to use the MIT-license or another one?

## Github

```{r, eval=FALSE}
devtools::use_github()
```
This creates your local github repository for the package. Go online to github.com/yourname to create your online repository with the same name. Commit and push your package.

```{r, eval=FALSE}
devtools::use_readme_rmd() 
devtools::use_travis() 
```
With these you create the README.Rmd and the travis.yml. 

The README.Rmd needs to be updated with your packagename in the "Travis-CI Build Status" (the url to your travis-website).

The travis.yml needs following changes:   

* repos: MRAN update date,     
* linux package dependencies      
* Rmd-name and path
* add: warnings_are_errors: false    (if you want to)


Remeber to locally build your package if you have created your own functions. 

## Folder structure
Create your analysis-folder (if you use it) and create there your Markdown.Rmd. Name it whatever you said in the travis.yml . 

Create the data-folder and whichever else you need.


## Circleci and Travis
Copy and paste the circle.yml from a working package into your package folder and edit the variables in the circle yml, especially the packagename.

Go to your websites on https://travis-ci.org/ and on https://circleci.com/ to create the connections to the github package. 

Paste in Dockerfile from a working package and edit ist. Things that need to change:  

* linux dependencies    
* package name,    
* markdown.Rmd-filename and path,    
* R-version, Rocker.verse - version

## Run the system
Commit everything and push it to Github.

Wait for the error message from Travis.

***Don't panic!***

Look at the error message and try to find out, what the problem was.
Good luck and when you succeed, don't forget to stick a yellow sticker to your laptop!

## Useful shell commands

For checking, committing and pushing files via the shell, use:
```{r, eval=FALSE}
$ git add filename.ext
$ git commit -m 'place comment here'
$ git push origin master
```


