---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# timetest

[![Travis-CI Build Status](https://travis-ci.org/benmarwick/timetest.svg?branch=master)](https://travis-ci.org/benmarwick/timetest)  [![Circle CI](https://circleci.com/gh/benmarwick/timetest.svg?style=shield&circle-token=:circle-token)](https://circleci.com/gh/benmarwick/timetest)

The goal of timetest is to see how long it takes to set up a basic researh compendium. We did the following steps:

1. devtools::create("pkgname")    


- edit the DESCRIPTION
- continuinously update Imports: with pkgs used in Rmd

2. devtools::use_mit_license()

- gives MIT licence, edit LICENSE fiel to add name

3. devtools::use_github(".", auth_token = "xxxx")         

- connect to github.com, get token from https://github.com/settings/tokens
- commit, push... maybe not, this is a bit flaky...

4. devtools::use_readme_rmd()     

- ready for to add markdon code to show travis and circle badges

5. devtools::use_travis()         

- go to the https://travis-ci.org/ to connect, 
- change: MRAN    
-- linux dependencies    
-- devtools::install() to install custom fns     
-- render Rmd    
-- warnings_are_error: false    

6. create analysis dir, and paper.Rmd and data/ dir

- in metadata yml block    
-- output: bookdown::word_document2    
-- bibliography:     
-- csl:      
- update travis.yml with path/name of Rmd    

7. paste in circle.yml           

- change pkg name in 3 places   
- go to https://circleci.com & add env vars
- add badge to readme.Rmd, knit to md   

8. paste in Dockerfile           

- edit dockerfile:     
-- set rocker/verse R version    
-- add linux dependencies    
-- update repo/pkg name   
-- update Rmd path/name    


## Installation

You can install timetest from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("benmarwick/timetest")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```
