---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# rrtools: Tools for Writing Reproducible Reseach in R

[![Travis-CI Build Status](https://travis-ci.org/benmarwick/rrtools.svg?branch=master)](https://travis-ci.org/benmarwick/rrtools)  

The goal of rrtools is to provide instructions, templates and functions for making a basic compendium suitable for doing reproducible research with R. This package documents the key steps and provides convenient functions for quickly creating a new research compendium. The approach is based generally on Kitzes et al. (2017), and more specifically on Marwick's (2017) work using the R package structure as the basis for a research compendium

rrtools gives you a template for doing scholarly writing in literate programming enviroment using R Markdown and bookdown. It also provides isolation of your computational enviroment using Docker, package versioning using MRAN, and continuous integration using Travis. It makes a convenient starting point for writing a journal article, report or thesis. 

This project was developed during the 2017 [ISAA Kiel](https://isaakiel.github.io/) Summer School on Reproducible Research in Landscape Archaeology at the Freie Universität Berlin (17-21 July). Special thanks to [Sophie C. Schmidt](https://github.com/SCSchmidt) for help. The convenience functions in this package are derived from similar functions in Hadley Wickham's `devtools` package.    

## Installation

You can install rrtools from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("benmarwick/rrtools")
```

## How to use

To create a reproducible research compendium using the rrtools approach, follow these steps (in RStudio, which we recommend):

#### 1. `devtools::create("pkgname")  `  

- this creates a basic R package with the name pkgname
- we need to double-click the `pkgname.Rproj` just created to open the new package project
-  edit the DESCRIPTION to give correct metadata
- then we continuinously update `Imports:` with names of pkgs used in Rmd, as we write the Rmd, this can be done with, for example, `devtools::use_package("dplyr", "imports")`

#### 2. `devtools::use_mit_license(copyright_holder = "My Name")`

- this gives MIT licence in DESCRIPTION, adds LICENSE file with our name in it

#### 3. `devtools::use_github(".", auth_token = "xxxx")`         

- connect to github.com, get token from https://github.com/settings/tokens
- commit, push... maybe not, this is a bit flaky...

#### 4. `devtools::use_readme_rmd(); devtools::use_code_of_conduct()`     

- this makes readme.Rmd, ready for to add markdown code to show travis badge
- we need to paste in test from CoC from fn output in console, ready for public contributions

#### 5. `rrtools::use_travis()`         

- this creates a minimal .travis.yml for us
- we need to go to the https://travis-ci.org/ to connect to our repo 
- we need to add environment variables to enable push of the Docker container to the Docker Hub

#### 6. `rrtools::use_analysis()` 

- this creates a top-level `analysis/` directory with the following contents:

```
analysis/
|
├── paper/
│   ├── paper.Rmd
│   ├── references.bib
│   └── journal-of-archaeological-science.csl
|
├── figures/
|
├── data/
│   ├── raw_data/
│   └── derived_data/
|
└──  templates
    ├── template.docx
    └── template.Rmd
```


- The `paper.Rmd` in `aanlysis/paper/` is ready to render with bookdown   
- The references.bib` file is empty, ready to insert reference details
- You can replace the supplied `csl` file with one from <https://github.com/citation-style-language/>    
- we recommend using the citr Addin and Zotero for high efficiency    
- we need to remember that when working in the Rmd writing code, we much update DESCTIPTION Imports: with pkg names used in the Rmd

#### 7. `rrtools::use_dockerfile()`           

- this will create a basic Dockerfile using `rocker/verse` as the base image   
- the version of R in your rocker container will match the version used when you run this function, for example `rocker/verse:3.4.0`  
- `rocker/verse` includes R, the tidyverse, RStudio, pandoc and LaTeX, so build times are very fast
- we need to edit dockerfile to add linux dependencies (if any) & modify which Rmd files are rendered when the container is made.     

#### 8. `devtools::use_testthat()`

- in case we have functions in R/, we need to have some tests to ensure they do what we want
- Create tests.R in tests/testhat/ and check http://r-pkgs.had.co.nz/tests.html for template

You should be able to follow these steps get a new research compendium repository connected to travis and ready to write in just a few minutes.  

## Future directions

We see scope for automation in these area:

- updating Imports: with `library()`, `require()` and :: calls in the Rmd    

## References

Kitzes, J., Turek, D., & Deniz, F. (Eds.). (2017). The Practice of Reproducible Research: Case Studies and Lessons from the Data-Intensive Sciences. Oakland, CA: University of California Press.

Marwick, B. (2017). Computational reproducibility in archaeological research: Basic principles and a case study of their implementation. _Journal of Archaeological Method and Theory_, 24(2), 424-450.

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
