# Colophon {-}

This document is set in [EB Garamond](https://github.com/georgd/EB-Garamond), [Source Code Pro](https://github.com/adobe-fonts/source-code-pro/) and [Lato](http://www.latofonts.com/lato-free-fonts/). The body text is set at 11pt with $\familydefault$. 

It was written in R Markdown and $\LaTeX$, and rendered into PDF using [huskydown](https://github.com/benmarwick/huskydown) and [bookdown](https://github.com/rstudio/bookdown). 

This document was typeset using the XeTeX typesetting system, and the [University of Washington Thesis class](http://staff.washington.edu/fox/tex/) class created by Jim Fox. Under the hood, the [University of Washington Thesis LaTeX template](https://github.com/UWIT-IAM/UWThesis) is used to ensure that documents conform precisely to submission standards. Other elements of the document formatting source code have been taken from the [Latex, Knitr, and RMarkdown templates for UC Berkeley's graduate thesis](https://github.com/stevenpollack/ucbthesis), and [Dissertate: a LaTeX dissertation template to support the production and typesetting of a PhD dissertation at Harvard, Princeton, and NYU](https://github.com/suchow/Dissertate)

The source files for this thesis, along with all the data files, have been organised into an R package, xxx, which is available at https://github.com/xxx/xxx. A hard copy of the thesis can be found in the University of Washington library.

This version of the thesis was generated on `r Sys.time()`. The repository is currently at this commit:

```{r echo = FALSE, eval = FALSE}
# I've set eval=FALSE to ensure Travis-CI can run
# if you're not using Travis-CI, then eval=TRUE will be fine
library(git2r)
if ( in_repository() ) {
       summary(commits()[[1]]) 
} else { 
       message("We are not in a git repository") 
}
```

The computational environment that was used to generate this version is as follows:

```{r echo = FALSE}
devtools::session_info()
```

