---
title: "Title Goes Here"
author:
  - Jane Doe:
      correspondence: "yes"
      email: janedoe@fosg.org
      orcid: 0000-0003-1689-0557
      institute:
        - fosg
        - fop
  - John Q. Doe:
      institute: fosg
      orcid: 0000-0003-1689-0558
  - Peder Ås:
      institute: fosg
      orcid: 0000-0003-1689-0559
  - Juan Pérez:
      orcid: 0000-0003-1689-0551
      institute:
        - name: Acme Corporation
  - Max Mustermann:
      orcid: 0000-0003-1689-0552
institute:
  - fosg:
      name: Formatting Open Science Group
      address: 23 Science Street, Eureka, Mississippi, USA
  - fop: Federation of Planets
title-block-published: "Last updated"  
date: now
date-format: long
format: 
  docx:
    reference-doc: "../templates/template.docx" # Insert path for the DOCX file
execute:
  echo: true
  warning: false
  message: false
  comment: "#>"
  fig-path: "../figures/"
  fig-dpi: 600
filters:
  - ../templates/scholarly-metadata.lua
  - ../templates/author-info-blocks.lua
  - ../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

<!-- This is the format for text comments that will be ignored during renderings. Do not put R code in these comments because it will not be ignored. -->

<!-- With the following code you can access and display values from the yml header above. -->

Keywords: `r rmarkdown::metadata$keywords`

Highlights: `r rmarkdown::metadata$highlights`

<!-- The actual document text starts here: -->

# Introduction

Here is a citation [@Marwick2017]

# Background

# Methods

# Results

<!-- Here's some example analysis code: -->

```{r}
#| label: get-data
#| eval: false
# Note the path that we need to use to access our data files when rendering this document
my_data <- read.csv(here::here('analysis/data/raw_data/my_csv_file.csv'))
```

```{r}
#| label: fig-demo-plot
#| fig-cap: "A plot of random numbers"
plot(rnorm(10))
```

@fig-demo-plot shows how we can have a caption and cross-reference for a plot. Note that figure label and cross-references must both be prefixed with `fig-`

```{r}
#| label: demo-inline-code
#| echo: false
x <- round(pi, 2)
```

Here is an example of inline code `r x` in the middle of a sentence.

# Discussion

# Conclusion

# Acknowledgements

<!-- The following line inserts a page break  -->

\newpage

# References

<!-- The following line ensures the references appear here for the MS Word or HTML output files, rather than right at the end of the document (this will not work for PDF files):  -->

::: {#refs}
:::

\newpage

### Colophon

This report was generated on `r Sys.time()` using the following computational environment and dependencies:

```{r}
#| label: colophon
#| cache: false

# which R packages and versions?
if ("devtools" %in% installed.packages()) devtools::session_info()
```

The current Git commit details are:

```{r}
# what commit is this file at? 
if ("git2r" %in% installed.packages() & git2r::in_repository(path = ".")) git2r::repository(here::here())  
```
